\documentclass[12pt]{article}
\input{preamble.tex}
\makenomenclature

\renewcommand{\nomname}{Nomenclature}

\renewcommand{\nompreamble}{The next list describes several symbols that will be later used within the body of the document}

\begin{document}

\input{cover.tex}

\clearpage
\pagestyle{plain}
\pagestyle{fancy}
\fancyhead[R]{} 
\fancyhead[L]{}
\clearpage

\spacing{1.2}
\pagenumbering{Roman}


\section*{Academic Integrity Declaration}

I declare that:

\begin{itemize}
  \item  the thesis submitted has been written by me alone.
  \item  the thesis submitted has not been previously submitted to this university or any
other.
\item  that all content, including primary and/or secondary data, is true to the best of my
knowledge.
\item  that all quotations and references have been duly acknowledged according to the
requirements of academic research.
\end{itemize} 

I understand that to knowingly submit work in violation of the above statement will be
considered by examiners as academic misconduct.



\clearpage
\pagestyle{plain}
\pagestyle{fancy}
\fancyhead[R]{ABSTRACT} 
\fancyhead[L]{}
\clearpage

\spacing{1.2}
\pagenumbering{Roman}


\section*{Abstract}
Flow control is used to limit the adverse impact of a system on climate change. Several techniques have been tested and evaluated in terms of the net power savings achieved. One of the flow control methods, spanwise oscillating wall flow control has been observed to provide a positive net power saving (Marusic et al., 2021). Due to the impacts of large and small-scale turbulence, high-fidelity computational fluid dynamics simulations are typically used to analyse flow control performance. However, these simulation methods are computationally costly, particularly when high Reynolds numbers are used. This study demonstrates the effectiveness of Generalised Richardson Extrapolation as an approach for reducing simulation resources. This study discovered that the Richardson Extrapolation can forecast the ideal values in both uncontrolled and controlled channel flow instances.  However, the extrapolation is limited to first-order statistics. When using Generalised Richardson Extrapolation to estimate second-order statistics, such as Reynolds stress tensor components, the result is massively overestimated. Additionally, the extrapolation outcomes are heavily influenced by coarse, medium, and fine resolution, necessitating rigorous control over the resolution of the sample models. Moreover, the results in this study demonstrate how Generalised Richardson Extrapolation functions in terms of predicting simulation results, as well as the algorithm's predicting performance. With this study, Generalised Richardson Extrapolation can be utilised in future DNS simulations to push the simulation limitations to flow regions that were not previously possible.




\clearpage
\pagestyle{plain}
\pagestyle{fancy}
\fancyhead[R]{ACKNOWLEDGEMENT} 
\fancyhead[L]{}
\clearpage

\spacing{1.2}
\pagenumbering{Roman}


\section*{Acknowledgement}
I would like to thank Dr. Tamás Józsa, my project supervisor, for his invaluable guidance in helping me develop my thesis project. His constant dedication and meticulous attention to detail have been crucial in completing this project. I am thankful that he gave me the chance to work on this project and beyond. 

I am also grateful to the Indonesian Ministry of Finance for providing financial support in the form of LPDP Scholarship for my studies at Cranfield University. I am able to conveniently support myself overseas owing to the funding.

In addition, I would like to thank my parents, and my little brother for the constant guidance and affection; Esa Panganti Widoretno for all of her support and encouragement; all of the PPI Cranfield members for making this place feel like home; and my classmates, in particular Kilyan Ocampo Cardenas, Shivane Patel, and Ricardo Ortega del Angel, for their invaluable assistance with the course's endless assignments.






%\addtocontents{toc}{\protect\thispagestyle{empty}} % for the first page
\clearpage
{
  \hypersetup{linkcolor=black}
  \pagestyle{fancy}
    \fancyhead[R]{TABLE OF CONTENTS} 
    \fancyhead[L]{}
  \tableofcontents
  \clearpage
    \pagestyle{fancy}
    \fancyhead[R]{LIST OF FIGURES} 
    \fancyhead[L]{}
  \addcontentsline{toc}{section}{List of Figures}
  \listoffigures
  \clearpage
    \pagestyle{fancy}
    \fancyhead[R]{LIST OF TABLES} 
    \fancyhead[L]{}
  \addcontentsline{toc}{section}{List of Tables}
  \listoftables
}

%\clearpage


%\clearpage
%\nomenclature{EFD}{Experimental Fluid Dynamics}
%%\nomenclature{CFD}{Computational Fluid Dynamics}
%\nomenclature{CRWTs}{Common Research Wind Tunnels}
%\nomenclature{RANS}{Reynolds-averaged Navier-Stokes }





%\addcontentsline{toc}{section}{Nomenclature}
%\printnomenclature
%\setlength{\parskip}{0.5cm}



\newpage
\pagenumbering{arabic}
\setcounter{page}{1}


\sloppy
\pagestyle{fancy}
\lhead{\small{}}
\rhead{{\small{LIST OF SYMBOLS AND ABBREVIATIONS}}}
\input{Nomenclature.tex}

%\nocite{*}
\clearpage
\pagestyle{fancy}
\lhead{\small{}}
\rhead{{\small{1. INTRODUCTION}}}
\input{Sections/1. Introduction}
\clearpage
\pagestyle{fancy}
\lhead{\small{}}
\rhead{{\small{2. METHODOLOGY}}}
\input{Sections/2. Methodology}
\clearpage
\pagestyle{fancy}
\lhead{\small{}}
\rhead{{\small{3. RESULTS AND DISCUSSION}}}
\input{Sections/3. Results}
\clearpage
\pagestyle{fancy}
\lhead{\small{}}
\rhead{{\small{4. CONCLUSIONS AND RECOMMENDATIONS}}}
\input{Sections/4. Conclusions and Recommendations}
%\clearpage
%\pagestyle{fancy}
%\lhead{\small{}}
%\rhead{{\small{5. RECOMMENDATIONS FOR FUTURE WORK}}}
%\input{Sections/5. Recommendations for Future Work}
\clearpage
\spacing{1.5}
\pagestyle{fancy}
\lhead{\small{}}
\rhead{{\small{BIBLIOGRAPHY}}}
\printbibliography[heading=bibintoc,title={References}]
\clearpage
\spacing{1.5}
\pagestyle{fancy}
\lhead{\small{}}
\rhead{{\small{APPENDIX}}}
\section*{APPENDIX}
\appendix
\input{Sections/Appendix/Annex_YZ slices deformationbaseline}
\end{document}

